\documentclass[curriculum-vitae-eng]{subfiles}

\begin{document}
	\section*{Education}
		\years{2021 - today} \textbf{Master's Degree} in Computer Science and Engineering at Alma Mater Studiorum University of Bologna, Campus of Cesena, Italy.\\
		
		\years{2018 - 2021} \textbf{Bachelor's Degree} in Computer Science and Engineering awarded with 106/110 on 7/10/2021 at Alma Mater Studiorum University of Bologna, Campus of Cesena, Italy.\\

		\years{2013 - 2018} \textbf{High school diploma} awarded with 90/100 at Liceo Scientifico A. Volta, Riccione (RN), Italy.
		
		\iffalse
		\subsection*{Exams taken during bachelor's degree}
			\begin{minipage}[t]{.47\textwidth}
				\exam{Algebra and Geometry}{26}
				\exam{Algorithms and Data Structures}{31}
				\exam{Mathematical Analysis}{27}
				\exam{Computer Achitectures}{29}
				\exam{Databases}{30}
				\exam{Computer Graphics}{28}
				\exam{Cryptography}{30}
				\exam{Physics}{31}
				\exam{High-Performance Computing}{30}
				\exam{Software engineering}{23}
			\end{minipage}
			\hfill
			\begin{minipage}[t]{.47\textwidth}
				\exam{Discrete Mathematics and Probability}{25}
				\exam{Numerical Algorithms}{22}
				\exam{Programming}{28}
				\exam{Object-oriented Programming}{28}
				\exam{Data-intensive Applications}{27}
				\exam{Network Programming}{28}
				\exam{Telecommunication networks}{23}
				\exam{Operations Research}{26}
				\exam{Operating Systems}{24}
				\exam{Web Technologies}{24}
			\end{minipage}
		\fi

		\subsection*{Bachelor's Degree Thesis}
			\begin{itemize}
				\item[-] {\large Title:} CUDA implementation of the Bellman-Ford algorithm.
				\item[$\star$] {\large Supervisor:} Prof. Moreno Marzolla
				\item {\large At:} Department of Computer Science and Engineering (DISI), University of Bologna, Italy
				\item[$\circ$] {\large Grade:} 106/110
				\item[] Design, development and performance evaluation of three different parallel implementations of the Bellman-Ford algorithm on CUDA-capable GPUs.
				\item[] Thesis available \href{https://amslaurea.unibo.it/24313}{here} (only in italian).
				\item[] Source code available \href{https://github.com/Ledmington/bellman-ford-cuda}{here}.
			\end{itemize}
		
		\subsection*{Internship}
			\begin{itemize}
				\item[-] {\large Title:} Development and perfomance evaluation of a parallel application designed for technical-scientific simulations.
				\item[$\star$] {\large Tutor:} Prof. Moreno Marzolla
				\item {\large At:} Department of Computer Science and Engineering (DISI), University of Bologna, Italy
				\item[] Development of an optimal sphere packing simulation regarding fuel particles inside a rocket's tank.
			\end{itemize}
		
		\iffalse
		\subsection*{Exams taken during Master's degree}
			{\small Last update: 27/01/2022}
			\medskip
			
			\begin{minipage}[t]{.47\textwidth}
				\exam{Machine Learning}{29}
			\end{minipage}
			\hfill
			\begin{minipage}[t]{.47\textwidth}
				% aggiungere qui futuri esami
			\end{minipage}
		\fi
\end{document}